### 2024-11-09 Reports/Final Report/sections/algorithm.tex
final documentation added

\Procedure{BeliefEmbeddingDerivation}{}
    \For{each participant}
        \State Use LLM to generate semantic embeddings for the statements
        \State Apply normalized coefficients (answers from the first phase) to the embeddings
        \State Aggregate the weighted embeddings to create an individual belief embedding
    \EndFor
\EndProcedure

@@

\Procedure{PredictUnanskedQuestions}{}
    \State Exclude a subset of answered questions from embedding calculation
    \State Use LLM to generate pivot statements of the omitted questions
    \State Use LLM to generate embeddings of the pivot statements
    \State Calculate the projection of each participant's belief embedding onto the target question's vector
    \State Estimate responses based on the distribution of projections
\EndProcedure

>>>>

\Procedure{BeliefEmbeddingDerivation}{}
    \For{each participant}
        \State Use the Sentence Transformer to generate semantic embeddings for the statements
        \State Apply normalized coefficients (answers from the first phase) to the embeddings
        \State Aggregate the weighted embeddings to create an individual belief embedding
    \EndFor
\EndProcedure

@@

\Procedure{PredictUnanskedQuestions}{}
    \State Exclude a subset of answered questions from embedding calculation
    \State Use the LLM to generate pivot statements of the omitted questions
    \State Use the Sentence Transformer to generate embeddings of the pivot statements
    \State Calculate the projection of each participant's belief embedding onto the target question's vector
    \State Estimate responses based on the distribution of projections
\EndProcedure

### 2024-11-09 Reports/Final Report/sections/appendix.tex
final documentation added

\section{Background}

\subsection{Survey Imputation}
Survey imputation is a crucial process in statistical analysis, used to address missing or incomplete data in survey responses. Missing data can introduce bias, reduce the statistical power of analyses, and compromise the validity of research findings \cite{little2019statistical, Schafer1999MultipleIA}. Imputation techniques help provide a complete dataset, enabling more accurate statistical inferences and robust conclusions.

@@

\newpage
\subsection{Large Language Models}

@@

\newpage

>>>>

\newpage
\section*{Appendix}
\subsection*{Results}

\begin{table}[H]
    \begin{tabular}{llrrr}
    \toprule
     &  & Mean Absolute Error & Cohen Kappa Score & Spearmanr \\
    Type & Variable &  &  &  \\
    \midrule
    \multirow[t]{12}{*}{\textbf{Unipolar}} & \textbf{polintr} & 0.883295 & 0.026453 & 0.238750 \\
    \textbf{} & \textbf{psppsgva} & 2.412656 & -0.011598 & 0.246687 \\
    \textbf{} & \textbf{actrolga} & 2.801398 & -0.001775 & 0.094148 \\
    \textbf{} & \textbf{psppipla} & 2.496940 & -0.012412 & 0.275624 \\
    \textbf{} & \textbf{cptppola} & 2.711854 & -0.000960 & 0.091823 \\
    \textbf{} & \textbf{trstprl} & 4.487281 & -0.007492 & 0.476543 \\
    \textbf{} & \textbf{trstlgl} & 3.201438 & 0.001075 & 0.324105 \\
    \textbf{} & \textbf{trstplc} & 2.329718 & 0.007078 & 0.322615 \\
    \textbf{} & \textbf{trstplt} & 4.929352 & -0.004681 & 0.396520 \\
    \textbf{} & \textbf{trstprt} & 4.805217 & -0.006087 & 0.412937 \\
    \textbf{} & \textbf{trstep} & 4.081178 & -0.011811 & 0.398581 \\
    \textbf{} & \textbf{trstun} & 3.682062 & -0.008092 & 0.326568 \\
    \cline{1-5}
    \multirow[t]{29}{*}{\textbf{Bipolar}} & \textbf{contplt} & 0.157835 & 0.001568 & 0.017867 \\
    \textbf{} & \textbf{donprty} & 0.067026 & 0.032551 & 0.076904 \\
    \textbf{} & \textbf{badge} & 0.061801 & 0.066551 & 0.134577 \\
    \textbf{} & \textbf{sgnptit} & 0.233863 & 0.017502 & 0.086000 \\
    \textbf{} & \textbf{pbldmna} & 0.059074 & 0.085699 & 0.163334 \\
    \textbf{} & \textbf{bctprd} & 0.211588 & 0.001169 & 0.018373 \\
    \textbf{} & \textbf{pstplonl} & 0.135863 & 0.033650 & 0.115589 \\
    \textbf{} & \textbf{volunfp} & 0.212746 & 0.028483 & 0.084148 \\
    \textbf{} & \textbf{clsprty} & 0.454186 & 0.001012 & 0.020542 \\
    \textbf{} & \textbf{lrscale} & 4.972976 & -0.001320 & 0.032543 \\
    \textbf{} & \textbf{stflife} & 2.463014 & -0.013502 & 0.177612 \\
    \textbf{} & \textbf{stfeco} & 3.876578 & -0.013553 & 0.332473 \\
    \textbf{} & \textbf{stfgov} & 4.419828 & -0.010696 & 0.324073 \\
    \textbf{} & \textbf{stfdem} & 3.173221 & -0.013464 & 0.433951 \\
    \textbf{} & \textbf{stfedu} & 2.557322 & 0.000234 & 0.278435 \\
    \textbf{} & \textbf{stfhlth} & 3.254164 & -0.009570 & 0.342289 \\
    \textbf{} & \textbf{gincdif} & 1.943013 & 0.001135 & -0.043765 \\
    \textbf{} & \textbf{freehms} & 2.154493 & 0.000020 & 0.128433 \\
    \textbf{} & \textbf{hmsfmlsh} & 0.983447 & -0.034093 & -0.224392 \\
    \textbf{} & \textbf{hmsacld} & 1.657760 & 0.002726 & 0.097818 \\
    \textbf{} & \textbf{euftf} & 3.741205 & -0.005271 & 0.205423 \\
    \textbf{} & \textbf{lrnobed} & 1.856650 & 0.002430 & -0.006947 \\
    \textbf{} & \textbf{loylead} & 1.521010 & -0.003442 & -0.087905 \\
    \textbf{} & \textbf{imsmetn} & 1.472540 & -0.013509 & 0.099564 \\
    \textbf{} & \textbf{imdfetn} & 0.958960 & 0.010774 & 0.169370 \\
    \textbf{} & \textbf{impcntr} & 1.489998 & -0.024520 & -0.167590 \\
    \textbf{} & \textbf{imbgeco} & 2.127999 & 0.021623 & 0.384305 \\
    \textbf{} & \textbf{imueclt} & 2.064119 & 0.012778 & 0.409174 \\
    \textbf{} & \textbf{imwbcnt} & 2.072170 & 0.002954 & 0.314608 \\
    \cline{1-5}
    \bottomrule
    \end{tabular}
    \caption{Summary of Results with Missing Values}
\end{table}

\begin{table}[H]
    \begin{tabular}{llrrr}
    \toprule
     &  & Mean Absolute Error & Cohen Kappa Score & Spearmanr \\
    Type & Variable &  &  &  \\
    \midrule
    \multirow[t]{12}{*}{\textbf{Unipolar}} & \textbf{polintr} & 0.968477 & 0.000303 & 0.184554 \\
    \textbf{} & \textbf{psppsgva} & 2.284846 & -0.010712 & 0.211624 \\
    \textbf{} & \textbf{actrolga} & 2.669605 & -0.001578 & 0.042211 \\
    \textbf{} & \textbf{psppipla} & 2.213117 & -0.012358 & 0.208630 \\
    \textbf{} & \textbf{cptppola} & 2.517598 & -0.002369 & 0.053133 \\
    \textbf{} & \textbf{trstprl} & 3.730582 & -0.012526 & 0.472565 \\
    \textbf{} & \textbf{trstlgl} & 2.994123 & 0.000621 & 0.315011 \\
    \textbf{} & \textbf{trstplc} & 1.798704 & 0.032405 & 0.351102 \\
    \textbf{} & \textbf{trstplt} & 3.758298 & -0.021041 & 0.448366 \\
    \textbf{} & \textbf{trstprt} & 4.217057 & -0.016612 & 0.413550 \\
    \textbf{} & \textbf{trstep} & 3.073800 & -0.010579 & 0.395895 \\
    \textbf{} & \textbf{trstun} & 3.093836 & -0.014292 & 0.384136 \\
    \cline{1-5}
    \multirow[t]{29}{*}{\textbf{Bipolar}} & \textbf{contplt} & 0.178922 & 0.000346 & 0.005706 \\
    \textbf{} & \textbf{donprty} & 0.079276 & 0.025499 & 0.071086 \\
    \textbf{} & \textbf{badge} & 0.071128 & 0.038593 & 0.095371 \\
    \textbf{} & \textbf{sgnptit} & 0.265010 & 0.008007 & 0.054114 \\
    \textbf{} & \textbf{pbldmna} & 0.068056 & 0.039456 & 0.101254 \\
    \textbf{} & \textbf{bctprd} & 0.247579 & 0.000272 & 0.006760 \\
    \textbf{} & \textbf{pstplonl} & 0.155012 & 0.018342 & 0.083775 \\
    \textbf{} & \textbf{volunfp} & 0.238362 & 0.013696 & 0.056084 \\
    \textbf{} & \textbf{clsprty} & 0.500634 & 0.000532 & 0.016317 \\
    \textbf{} & \textbf{lrscale} & 4.889868 & -0.001741 & 0.041140 \\
    \textbf{} & \textbf{stflife} & 1.784813 & 0.002401 & 0.146555 \\
    \textbf{} & \textbf{stfeco} & 3.191678 & -0.014983 & 0.297870 \\
    \textbf{} & \textbf{stfgov} & 3.905697 & -0.012772 & 0.271658 \\
    \textbf{} & \textbf{stfdem} & 2.481600 & 0.003359 & 0.382774 \\
    \textbf{} & \textbf{stfedu} & 2.157016 & 0.012808 & 0.265109 \\
    \textbf{} & \textbf{stfhlth} & 3.185734 & -0.010900 & 0.347053 \\
    \textbf{} & \textbf{gincdif} & 1.899152 & 0.000413 & -0.014047 \\
    \textbf{} & \textbf{freehms} & 2.207106 & -0.001243 & 0.133389 \\
    \textbf{} & \textbf{hmsfmlsh} & 0.957991 & -0.033302 & -0.225402 \\
    \textbf{} & \textbf{hmsacld} & 1.710279 & 0.001587 & 0.073138 \\
    \textbf{} & \textbf{euftf} & 3.672010 & -0.004350 & 0.202250 \\
    \textbf{} & \textbf{lrnobed} & 1.825419 & 0.002235 & -0.034651 \\
    \textbf{} & \textbf{loylead} & 1.766981 & -0.009832 & -0.107330 \\
    \textbf{} & \textbf{imsmetn} & 1.656315 & -0.015923 & 0.073245 \\
    \textbf{} & \textbf{imdfetn} & 1.332131 & -0.028476 & 0.149849 \\
    \textbf{} & \textbf{impcntr} & 1.574234 & -0.021680 & -0.192748 \\
    \textbf{} & \textbf{imbgeco} & 2.031523 & 0.025904 & 0.374692 \\
    \textbf{} & \textbf{imueclt} & 2.005944 & 0.017193 & 0.414707 \\
    \textbf{} & \textbf{imwbcnt} & 1.982368 & 0.005425 & 0.317069 \\
    \cline{1-5}
    \bottomrule
    \end{tabular}
    \caption{Summary of Results without Missing Values}
\end{table}

\begin{table}[H]
    \begin{tabular}{lrrr}
    \toprule
     & Mean Absolute Error & Cohen Kappa Score & Spearmanr \\
    Type &  &  &  \\
    \midrule
    \textbf{Bipolar} & 1.736360 & 0.006204 & 0.135062 \\
    \textbf{Unipolar} & 3.235199 & -0.002525 & 0.300408 \\
    \bottomrule
    \end{tabular}
    \caption{Means with Missing Values}
\end{table}

\begin{table}[H]
    \begin{tabular}{lrrr}
    \toprule
     & Mean Absolute Error & Cohen Kappa Score & Spearmanr \\
    Type &  &  &  \\
    \midrule
    \textbf{Bipolar} & 1.655925 & 0.002099 & 0.117475 \\
    \textbf{Unipolar} & 2.776670 & -0.005728 & 0.290065 \\
    \bottomrule
    \end{tabular}
    \caption{Means without Missing Values}
\end{table}

\subsection*{Literature Reviews}

\subsubsection*{Survey Imputation}
Survey imputation is a crucial process in statistical analysis, used to address missing or incomplete data in survey responses. Missing data can introduce bias, reduce the statistical power of analyses, and compromise the validity of research findings \cite{little2019statistical, Schafer1999MultipleIA}. Imputation techniques help provide a complete dataset, enabling more accurate statistical inferences and robust conclusions.

@@

\subsubsection*{Large Language Models}

@@
